Nonparametric Goodness-of-Fit Tests for Discrete Null Distributions

### 2011-08-27 rjournal/AE.tex
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/ks-test@74 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

data:  c(0, 1) 
D = 0.5, $p$-value = 0.5
alternative hypothesis: two-sided 
\end{Soutput}
\end{Schunk}
Instead, the value of $D$ given in equation (1)
should be 0 and the associated $p$-value should be 1.  
Our revision of \code{ks.test()}
fixes this problem when the user provides a discrete distribution:
\begin{Schunk} 
\begin{Sinput}
> library(ks.test)
> dgof::ks.test(c(0, 1), ecdf(c(0, 1)))
\end{Sinput}
\begin{Soutput}
	One-sample Kolmogorov-Smirnov test

data:  c(0, 1) 
D = 0, $p$-value = 1
alternative hypothesis: two-sided 
\end{Soutput}
\end{Schunk}

@@

data:  x 
D = 0.08, $p$-value = 0.9354
alternative hypothesis: two-sided 
\end{Soutput}
\end{Schunk}
Next, we conduct the default one-sided test, where Conover's method
provides the exact $p$-value (up to the numerical precision of the
implementation):
\begin{Schunk}
\begin{Sinput}
> dgof::ks.test(x, ecdf(1:10),
+   alternative = "g")
\end{Sinput}
\begin{Soutput}
	One-sample Kolmogorov-Smirnov test

data:  x 
D^+ = 0.04, $p$-value = 0.7731
alternative hypothesis:
the CDF of x lies above the null hypothesis 
\end{Soutput}
\end{Schunk}
In contrast, the option \code{exact=FALSE} results in the
$p$-value obtained by applying the classical Kolmogorov-Smirnov
test, resulting in a conservative $p$-value:
\begin{Schunk}
\begin{Sinput}
> dgof::ks.test(x, ecdf(1:10),
+   alternative = "g", exact = FALSE)
\end{Sinput}
\begin{Soutput}
	One-sample Kolmogorov-Smirnov test

data:  x 
D^+ = 0.04, $p$-value = 0.9231
alternative hypothesis:
the CDF of x lies above the null hypothesis 
\end{Soutput}
\end{Schunk}
The $p$-value may also be estimated via a Monte Carlo simulation:
\begin{Schunk}
\begin{Sinput}
> dgof::ks.test(x, ecdf(1:10),
+   alternative = "g",
+   simulate.p.value=TRUE, B=10000)
\end{Sinput}
\begin{Soutput}
	One-sample Kolmogorov-Smirnov test

@@

data:  rep(1, 3) 
D = 0.6667, $p$-value = 0.07407
alternative hypothesis: two-sided 
\end{Soutput}
\end{Schunk}
If, instead, either \code{exact=FALSE} is used with the new
\code{ks.test()} function, or if the original \code{stats::ks.test()}
is used, the reported $p$-value is 0.1389 even though the test statistic
is the same.

@@

data:  x 
W2 = 0.057, $p$-value = 0.8114
alternative hypothesis: Two.sided 
\end{Soutput}
\begin{Sinput}
> cvm.test(x, ecdf(1:10), type = "A2")
\end{Sinput}
\begin{Soutput}
	Cramer-von Mises - A2

data:  x 
A2 = 0.3969, $p$-value = 0.75
alternative hypothesis: Two.sided 
\end{Soutput}
\end{Schunk}

@@

data:  y 
U2 = 0.0094, $p$-value = 0.945
alternative hypothesis: Two.sided 
\end{Soutput}
\begin{Sinput}
> z <- y%%4 + 1
> cvm.test(z, ecdf(1:4), type = 'U2')
\end{Sinput}
\begin{Soutput}
	Cramer-von Mises - U2

data:  z 
U2 = 0.0094, $p$-value = 0.945
alternative hypothesis: Two.sided 
\end{Soutput}
\end{Schunk}
In contrast, the Kolmogorov-Smirnov or the standard Cram\'{e}r-von Mises tests
produce different results after such a reordering. For example, the default
Cram\'{e}r-von Mises test yields $p$-values of 0.8237 and 0.9577 with the original
and transformed data \code{y} and \code{z}, respectively.

>>>>

data:  c(0, 1) 
D = 0.5, p-value = 0.5
alternative hypothesis: two-sided 
\end{Soutput}
\end{Schunk}
Instead, the value of $D$ given in equation (1)
should be 0 and the associated $p$-value should be 1.  
Our revision of \code{ks.test()}
fixes this problem when the user provides a discrete distribution:
\begin{Schunk} 
\begin{Sinput}
> library(ks.test)
> dgof::ks.test(c(0, 1), ecdf(c(0, 1)))
\end{Sinput}
\begin{Soutput}
	One-sample Kolmogorov-Smirnov test

data:  c(0, 1) 
D = 0, p-value = 1
alternative hypothesis: two-sided 
\end{Soutput}
\end{Schunk}

@@

data:  x 
D = 0.08, p-value = 0.9354
alternative hypothesis: two-sided 
\end{Soutput}
\end{Schunk}
Next, we conduct the default one-sided test, where Conover's method
provides the exact $p$-value (up to the numerical precision of the
implementation):
\begin{Schunk}
\begin{Sinput}
> dgof::ks.test(x, ecdf(1:10),
+   alternative = "g")
\end{Sinput}
\begin{Soutput}
	One-sample Kolmogorov-Smirnov test

data:  x 
D^+ = 0.04, p-value = 0.7731
alternative hypothesis:
the CDF of x lies above the null hypothesis 
\end{Soutput}
\end{Schunk}
In contrast, the option \code{exact=FALSE} results in the
$p$-value obtained by applying the classical Kolmogorov-Smirnov
test, resulting in a conservative $p$-value:
\begin{Schunk}
\begin{Sinput}
> dgof::ks.test(x, ecdf(1:10),
+   alternative = "g", exact = FALSE)
\end{Sinput}
\begin{Soutput}
	One-sample Kolmogorov-Smirnov test

data:  x 
D^+ = 0.04, p-value = 0.9231
alternative hypothesis:
the CDF of x lies above the null hypothesis 
\end{Soutput}
\end{Schunk}
The $p$-value may also be estimated via a Monte Carlo simulation:
\begin{Schunk}
\begin{Sinput}
> dgof::ks.test(x, ecdf(1:10),
+   alternative = "g",
+   simulate.p.value=TRUE, B=10000)
\end{Sinput}
\begin{Soutput}
	One-sample Kolmogorov-Smirnov test

@@

data:  rep(1, 3) 
D = 0.6667, p-value = 0.07407
alternative hypothesis: two-sided 
\end{Soutput}
\end{Schunk}
If, instead, either \code{exact=FALSE} is used with the new
\code{ks.test()} function, or if the original \code{stats::ks.test()}
is used, the reported $p$-value is 0.1389 even though the test statistic
is the same.

@@

data:  x 
W2 = 0.057, p-value = 0.8114
alternative hypothesis: Two.sided 
\end{Soutput}
\begin{Sinput}
> cvm.test(x, ecdf(1:10), type = "A2")
\end{Sinput}
\begin{Soutput}
	Cramer-von Mises - A2

data:  x 
A2 = 0.3969, p-value = 0.75
alternative hypothesis: Two.sided 
\end{Soutput}
\end{Schunk}

@@

data:  y 
U2 = 0.0094, p-value = 0.945
alternative hypothesis: Two.sided 
\end{Soutput}
\begin{Sinput}
> z <- y%%4 + 1
> cvm.test(z, ecdf(1:4), type = 'U2')
\end{Sinput}
\begin{Soutput}
	Cramer-von Mises - U2

data:  z 
U2 = 0.0094, p-value = 0.945
alternative hypothesis: Two.sided 
\end{Soutput}
\end{Schunk}
In contrast, the Kolmogorov-Smirnov or the standard Cram\'{e}r-von Mises tests
produce different results after such a reordering. For example, the default
Cram\'{e}r-von Mises test yields $p$-values of 0.8237 and 0.9577 with the original
and transformed data \code{y} and \code{z}, respectively.
